---
title: "TIL"
author: "Jessica Lavery"
date: "2/7/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Reshape data from multiple columns to 1 row per column (rather than rbind with renames; 2/7/2021)

```{r}
tibble(low = c(1, 2, 3),
       medium = c(4, 5, 6),
       high = c(7, 8, 9)) %>% 
  # id.vars specify the variables that are NOT going to go from multiple columns to a long format in a single column
  reshape2::melt(#id.vars = c("low", "medium", "high"),
                 value.name = "value") 
```


## Expand by Frequency (2/1/2021)

Starting with a summarized dataset, expand to 1 record per unit. 

```{r}
tibble(outc = c(rep(0, 10), rep(1, 10)),
       freq = abs(round(10*rnorm(20))) + 1) %>% 
  vcdExtra::expand.dft(freq = "freq") %>% 
  nrow()
```

## Rename columns systematically (3/1/2021)

```{r}
# add "_pt" suffix to select varaible names
# can modify to add a prefix instead
tibble(n_tm_1 = c(1, 2),
       n_tm_2 = c(3, 4)) %>% 
  rename_with(~str_c(., "_pt"), .cols = starts_with("n_tm")) %>% 
  names()
```

## Select minimum value, including ties (3/7/2021)

```{r}
tibble(groups = c("a", "a", "a", "b", "b"),
       num = c(1, 1, 2, 3, 4)) %>% 
  group_by(groups) %>% 
  slice_min(num, with_ties = TRUE)
```

## Select minimum value if available, otherwise NA if minimum value is missing

Doesn't pick up NA as a min for group a, picks up the actual minimum 

```{r}
tibble(groups = c("a", "a", "a", "a", "b", "b", "c"),
       num = c(1, 1, NA, 2, 3, 4, NA)) %>% 
  group_by(groups) %>% 
  slice(which.min(num), is.na(num))
```

## Two equivalent ways to specify binomial model (3/27/21)

```{r}
# https://stats.stackexchange.com/questions/189115/fitting-a-binomial-glmm-glmer-to-a-response-variable-that-is-a-proportion-or-f

# cbind columns for outcome yes, outcome no
# where outcome no = total # tries - total # yeses
glmer(cbind(outcome_value, rep(7, nrow(data_long_adhere)) - outcome_value) ~ 
        age_cat + race + gender2 + formulation + 
        #race*formulation +# gender2*formulation +
        (1 | ptid),
      family = "binomial",
      # weight = rep(7, nrow(data_long_adhere)),
      data = data_long_adhere
) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  add_global_p()

# outcome / total number tries
# weight statement = total number tries
glmer(outcome_value / rep(7, nrow(data_long_adhere)) ~ 
        age_cat + race + gender2 + formulation +# gender2*formulation +
        (1 | ptid),
      family = "binomial",
      weight = rep(7, nrow(data_long_adhere)),
      data = data_long_adhere
) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  add_global_p()
```

