---
title: "TIL"
author: "Jessica Lavery"
date: "2/7/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Common legend for multiple ggplots

```{r}
# https://stackoverflow.com/questions/13649473/add-a-common-legend-for-combined-ggplots

library(ggplot2)
library(gridExtra)

# won't work b/c didn't save the data, just for an example
p1 <- ggplot(df1, aes(x=x, y=y,colour=group)) + geom_point(position=position_jitter(w=0.04,h=0.02),size=1.8) + theme(legend.position="bottom")
p2 <- ggplot(df2, aes(x=x, y=y,colour=group)) + geom_point(position=position_jitter(w=0.04,h=0.02),size=1.8)

# extract legend
# https://github.com/hadley/ggplot2/wiki/Share-a-legend-between-two-ggplot2-graphs
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend <- g_legend(p1)

# combine into single plot with a common legend
grid.arrange(arrangeGrob(p1 + theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         nrow=1),
             mylegend, nrow=2,heights=c(10, 1))
```

## Plot ggsurvplot objects side by side; 6/13/2021

```{r}
library(survival)
library(survminer)

# example data frame
xx = data.frame(stim = c(2, 1:4),
                sts = rep(1, 5))

# survfit
oo = survfit(Surv(time = stim, event = sts) ~ 1, data = xx)

# create two ggplot objects
plot1<- ggsurvplot(fit = oo, xlim=c(-2, 5))

plot2<- ggsurvplot(fit = oo, xlim=c(-2, 5))

# have to use $plot 
# option 1: gridarrange
ggarrange(plotlist=list(plot1$plot,plot2$plot),
          labels = c("A", "B"),
          ncol = 2, nrow = 1)

# option 2: patchwork
library(patchwork)
plot1$plot + plot2$plot

# option 3: cowplot
library(cowplot)
plot_grid(plot1$plot, plot2$plot)
```

## Select variables matching specific criteria; 5/10/2021

```{r}
# select based on something like 
# matches("drugs_drug_[[:digit:]]")
# which will only include drugs_drug_1 to drugs_drug_5 without picking up the drugs_drug_oth.
```

## Reshape data from multiple columns to 1 row per column (rather than rbind with renames; 2/7/2021)

```{r}
tibble(low = c(1, 2, 3),
       medium = c(4, 5, 6),
       high = c(7, 8, 9)) %>% 
  # id.vars specify the variables that are NOT going to go from multiple columns to a long format in a single column
  reshape2::melt(#id.vars = c("low", "medium", "high"),
                 value.name = "value") 
```


## Expand by Frequency (2/1/2021)

Starting with a summarized dataset, expand to 1 record per unit. 

```{r}
tibble(outc = c(rep(0, 10), rep(1, 10)),
       freq = abs(round(10*rnorm(20))) + 1) %>% 
  vcdExtra::expand.dft(freq = "freq") %>% 
  nrow()
```

## Rename columns systematically (3/1/2021)

```{r}
# add "_pt" suffix to select varaible names
# can modify to add a prefix instead
tibble(n_tm_1 = c(1, 2),
       n_tm_2 = c(3, 4)) %>% 
  rename_with(~str_c(., "_pt"), .cols = starts_with("n_tm")) %>% 
  names()
```

## Select minimum value, including ties (3/7/2021)

```{r}
tibble(groups = c("a", "a", "a", "b", "b"),
       num = c(1, 1, 2, 3, 4)) %>% 
  group_by(groups) %>% 
  slice_min(num, with_ties = TRUE)
```

## Select minimum value if available, otherwise NA if minimum value is missing

Doesn't pick up NA as a min for group a, picks up the actual minimum 

```{r}
tibble(groups = c("a", "a", "a", "a", "b", "b", "c"),
       num = c(1, 1, NA, 2, 3, 4, NA)) %>% 
  group_by(groups) %>% 
  slice(which.min(num), is.na(num))
```

## Two equivalent ways to specify binomial model (3/27/21)

```{r}
# https://stats.stackexchange.com/questions/189115/fitting-a-binomial-glmm-glmer-to-a-response-variable-that-is-a-proportion-or-f

# cbind columns for outcome yes, outcome no
# where outcome no = total # tries - total # yeses
glmer(cbind(outcome_value, rep(7, nrow(data_long_adhere)) - outcome_value) ~ 
        age_cat + race + gender2 + formulation + 
        #race*formulation +# gender2*formulation +
        (1 | ptid),
      family = "binomial",
      # weight = rep(7, nrow(data_long_adhere)),
      data = data_long_adhere
) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  add_global_p()

# outcome / total number tries
# weight statement = total number tries
glmer(outcome_value / rep(7, nrow(data_long_adhere)) ~ 
        age_cat + race + gender2 + formulation +# gender2*formulation +
        (1 | ptid),
      family = "binomial",
      weight = rep(7, nrow(data_long_adhere)),
      data = data_long_adhere
) %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  add_global_p()
```

